\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex
GRB100424A, GRB100425A, GRB100615A and GRB100621A
Notes on individuals bursts

	\subsection{GRB100205A}
	Observed 3 days after the \textit{Swift} trigger. No afterglow or host detected in 10.8 ks. GRB likely located at high redshift\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10399.gcn3}}.

@@

	\subsection{GRB100316B (z = 1.180)}
	The data presented here also formed the basis of GCN \#
	10495\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10495.gcn3}}.
	Observations started 44 minutes after the \textit{Swift} trigger and has a
	total exposure time of 2.4 ks.
	Absorption features from \feii, \alii, \aliii,	\mgii~and \mgi~are well detected against the afterglow continuum at $z = 1.180$. Additionally, strong absorption lines from \feii~and \mgii~from an intervening system are found at $z = 1.063$.

@@

	\subsection{GRB100724A* (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow
	continuum at a common redshift of $z = 1.288$.
	This burst has been flux calibrated using the master response function and is
	not a part of the statistical sample.

>>>>

	\subsection{GRB100205A}
	Observed 3 days after the \textit{Swift} trigger. No afterglow or host detected in 10.8 ks. GRB likely located at high redshift\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10399.gcn3}}. The spectrum has not otherwise been published previously.

@@

	\subsection{GRB100316B (z = 1.180)}
	The data presented here also formed the basis of GCN \#
	10495\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10495.gcn3}}.
	The spectrum has not otherwise been published previously.
	Observations started 44 minutes after the \textit{Swift} trigger and has a
	total exposure time of 2.4 ks.
	Absorption features from \feii, \alii, \aliii,	\mgii~and \mgi~are well detected against the afterglow continuum at $z = 1.180$. Additionally, strong absorption lines from \feii~and \mgii~from an intervening system are found at $z = 1.063$.

@@

	\subsection{GRB100424A (z=2.465)}
	The data presented here also formed the basis of GCN \#
	14291\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14291.gcn3}}.
	The spectrum has not otherwise been published previously.
	Observations carried out, long after the burst has faded.  Emission lines from
	the host are detected at $z=2.465$.

	\subsection{GRB100425A (z=1.1755)}
	The data presented here also formed the basis of GCN \#
	10684\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10684.gcn3}} and is used in
	\citet{Skuladottir2010}, but not published elsewhere.
	Observations started 4 hours after the \textit{Swift} trigger, totaling 2.4 ks. 
	Absorption features from \mgii~and \feii~in the afterglow continuum are
	detected at $z=1.1755$.

	\subsection{GRB100615A (z=1.398)}
	The data presented here also formed the basis of GCN \#
	14264\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14264.gcn3}}, 
	but not published elsewhere.
	Host observation of a dark burst\citep{DElia2011} taken long after the afterglow has faded. Emission lines from the host belonging to \oii, \neiii, \oiii~and \ha~are detected at a common redshift of $z=1.398$.

	\subsection{GRB100621A (z=0.542)}
	The data presented here also formed the basis of GCN \#
	10876\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10876.gcn3}}, 
	but not published elsewhere.
	Beginning 7.1 hours after the GRB, 2.4 ks observations reveal emission lines from \oii, \hb~and \oiii~at a common redshift of $z=0.542$.

	\subsection{GRB100724A* (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow
	continuum at a common redshift of $z = 1.288$.
	This is not a part of the statistical sample.
